### 2016-08-16 ch02-qlogms/excitation-design.tex
Small changes for formatting
 - Moving labels in figures
 - Some negative spaces in formulas
Tweak for better pagination

\subsection{Sums of Second Order Systems}
This section extends the previous section to more general systems than second order.
Consider a system
\begin{align}
G(s,\theta) &= \sum_{i=1}^{K} G_i(s,\theta_i)
             =\sum_{i=1}^{K}  \frac{1}
                                   {   \frac{s^2}{\wn[i]^2}
                                    + 2\frac{\damping[i]}{\wn[i]}s
                                    + 1},\\
\theta_i&=[\wn[i]\;\damping[i]]^{\T}.
\label{eq:excitation:sumSys}
\end{align}
The systems  $G_i$ will be called the \emph{sub-systems} of $G$. 
Without loss of generality, we assume that $\wn[1] < \wn[2] < \cdots < \wn[K]$. 
To properly identify the system $G$, excitation is required such that all sub-systems are properly excited, regardless of their individual resonance frequencies.
%TODO: very limited model (K=1). Comment.

@@

\begin{figure}
\centering
\setlength\figurewidth{0.68\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/coupling.tikz}
\caption[Relative amplitudes of the off-diagonal blocks of the Fisher information matrix.]{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
         The different plots are for different separations of the resonance frequencies, from $4\wdB$ to $64\wdB$.
         The arrow indicates the direction of increasing separation.}
\label{fig:excitation:coupling}
\end{figure}

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/misalign.tikz}
    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic generalized multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
    The $3\unit{dB}$ bandwidth ($\wdB$) around the peak frequency $\wM$ of the system is highlighted.}
    \label{fig:excitation:misalignment-logms}
  \end{figure}

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.75\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (see \eqref{eq:excitation:optimAlpha}).}
    \label{fig:excitation:worstCaseBeta}
  \end{figure}

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.75\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
             grid multisines and systems with different peak amplitudes.}
    \label{fig:excitation:worstCaseAlpha}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.5\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/SignalAndSystem.tikz}
    \caption[System with highlighted bandwidth and multisine components.]{Depiction of the transfer function $G$ of a second order system, along with a logarithmic multisine excitation $U$ for $\alpha = \alpha^{\star}$. The circled sine components lie within the $3 \unit{dB}$ bandwidth of $G$.}%
    \label{fig:excitation:signalAndSystem}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping02-cmp.tikz}
    \caption[Simulated \glsentryshortpl{FRF} of systems with damping $0.2$ for different excitation signals.]{%
       \Glspl{FRF} for different second order systems with constant damping $\damping=0.2$ but different resonance frequencies. 
       Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping02}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping005-cmp.tikz}
    \caption[Simulated \glsentryshortpl{FRF} of systems with damping $0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies. 
    Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping005}
  \end{figure}

@@

    \begin{figure}%
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption[Measurements of all BK1613 octave filters using different excitation signals.]{Measured FRFs of the different \bruelkjaer{} 1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
      \label{fig:excitation:measurements}
    \end{figure}

>>>>

\subsection{Sums of Second Order Systems}
This section extends the previous section to more general systems than second order.
Consider a system
\begin{align}
G(s,\theta) &= \sum_{i=1}^{K} G_i(s,\theta_i)
             =\sum_{i=1}^{K}  \frac{1}
                                   {   \frac{s^2}{\wn[i]^2}
                                    + 2\frac{\damping[i]}{\wn[i]}s
                                    + 1},\\
\theta_i&=[\wn[i]\;\damping[i]]^{\T}.
\label{eq:excitation:sumSys}
\end{align}
The systems  $G_i$ will be called the \emph{sub-systems} of $G$. 
Without loss of generality, we assume that $\wn[1] < \wn[2] < \cdots < \wn[K]$. 
To properly identify the system $G$, excitation is required such that all sub-systems are properly excited, regardless of their individual resonance frequencies.

@@

\begin{figure}
\centering
\setlength\figurewidth{0.68\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/coupling.tikz}
\caption[Relative amplitudes of the off-diagonal blocks of the Fisher information.]{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
         The different plots are for different separations of the resonance frequencies, from $4\wdB$ to $64\wdB$.
         The arrow indicates the direction of increasing separation.}
\label{fig:excitation:coupling}
\end{figure}

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/misalign.tikz}
    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
    The $3\unit{dB}$ bandwidth ($\wdB$) around the peak frequency $\wM$ of the system is highlighted.}
    \label{fig:excitation:misalignment-logms}
  \end{figure}

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.7\columnwidth}
      \setlength\figureheight{0.62\figurewidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (see \eqref{eq:excitation:optimAlpha}).}
    \label{fig:excitation:worstCaseBeta}
    \vspace{-0.5em} % to make the figures fit on a page
  \end{figure}

    \begin{figure}
    \vspace{-0.5em} % to make the figures fit on a page
    \centering
      \setlength\figurewidth{0.7\columnwidth}
      \setlength\figureheight{0.62\figurewidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic grid multisines and systems with different peak amplitudes.}
    \label{fig:excitation:worstCaseAlpha}
  \end{figure}

@@

@@

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping02-cmp.tikz}
    \caption[Simulated \glsentryshortpl{FRF} of systems (damping $\xi=0.2$) for different excitations.]{%
       \Glspl{FRF} for different second order systems with constant damping $\damping=0.2$ but different resonance frequencies. 
       Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping02}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping005-cmp.tikz}
    \caption[Simulated \glsentryshortpl{FRF} of systems (damping $\xi=0.05$) for different excitations.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies. 
    Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping005}
  \end{figure}

@@

    \begin{figure}[t]
    \centering
      \setlength\figurewidth{0.75\columnwidth}
      \setlength\figureheight{0.62\figurewidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption[Measurements of all BK1613 octave filters using different excitation signals.]{Measured FRFs of the different \bruelkjaer{} 1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
      \label{fig:excitation:measurements}
    \end{figure}

### 2016-08-16 ch03-lrm/nonparametric.tex
Tweak for better pagination

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-60.tikz}
  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:hiSNR}
\end{figure}

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-40.tikz}
  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:midSNR}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-20.tikz}
  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=20\unit{dB}$.
  The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:lowSNR}
\end{figure}

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-10.tikz}
 \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=10\unit{dB}$. The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:terribleSNR}
\end{figure}

@@

\section{Smoothing the \glsentryshort{FRF} by Impulse Response Truncation}
\label{sec:nonparametric:truncation}
\sectionBasedOn{Lumori2014TIM}

>>>>

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-60.tikz}
  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. \\
  The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:hiSNR}
\end{figure}

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-40.tikz}
  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. \\
  The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:midSNR}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-20.tikz}
  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=20\unit{dB}$.\\
  The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:lowSNR}
\end{figure}

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-10.tikz}
 \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=10\unit{dB}$. \\
 The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:terribleSNR}
\end{figure}

@@

\newpage
\section{Smoothing the \glsentryshort{FRF} by Impulse Response Truncation}
\label{sec:nonparametric:truncation}
\sectionBasedOn{Lumori2014TIM}

### 2016-08-16 ch05-initvals/initial-values.tex
Tweak for better pagination

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/successRates.tikz}
 \caption[Simulated success rate of the different initialization schemes for varying \glsentryshort{SNR}.]{The success rate $\successRate$  obtained using the smoothers, i.e. $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems. The $95\%$ confidence intervals~\eqref{eq:initvals:Binomial:CI} are indicated by bars.}
  \label{fig:successRateVS_SNR36N3dB}
\end{figure}

@@

\begin{figure}
  \centering
  % \ref{leg:init:secondBest}
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/figs/special-histogram.tikz}
  \caption[Performance degradation/enhancement for selecting the second best model.]{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
  The markers show individual observations and the boxes show the \gls{IQR}.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  On average there is little to gain or lose from using $\model{RFIR}$ instead of $\model{best}$.
  For $\model{exist}$ and $\model{trunc}$, the situation is a lot less favorable.
  }
  \label{fig:init:histogramEnhancement}
\end{figure}

>>>>

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/successRates.tikz}
 \caption[Simulated success rate of the initialization schemes for varying \glsentryshort{SNR}.]{The success rate $\successRate$  obtained using the smoothers, i.e. $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems. The $95\%$ confidence intervals~\eqref{eq:initvals:Binomial:CI} are indicated by bars.}
  \label{fig:successRateVS_SNR36N3dB}
\end{figure}

@@

\begin{figure}
  \centering
  % \ref{leg:init:secondBest}
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/figs/special-histogram.tikz}
  \caption[Performance penalty for selecting the second best model.]{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
  The markers show individual observations and the boxes show the \gls{IQR}.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  On average there is little to gain or lose from using $\model{RFIR}$ instead of $\model{best}$.
  For $\model{exist}$ and $\model{trunc}$, the situation is a lot less favorable.
  }
  \label{fig:init:histogramEnhancement}
\end{figure}
